---
title: "Tutorial Mike"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


<!-- NOTE: This example and text is taken verbatim from DataCamp, starting with Variable assignment. The text must change. -->

## Getting started

### Exercise 

*Comments*

R makes use of the # sign to add comments, so that you and others can understand what the R code is about. Just like Twitter! Comments are not run as R code, so they will not influence your result. For example, Calculate 3 + 4 in the example below is a comment.

When you press the "Run Code" button, nothing happens. R ignores everything on the line after the # sign. Use comments liberally in your code. Use comments to remind yourself what your code chunks do.  

```{r comments, exercise=TRUE}
# Calculate 3 + 4

```

*Sample Code*

Here is some sample code that adds 3 + 4. To execute the code, press the blue "Run Code" button to the right. The result (7) should appear below the code.

```{r three-plus-four, exercise=TRUE}
3 + 4

```

You can edit and add code as required by the instructions. For example, change the code to add 6 + 12, then add a second line to subtract 3 from 15.

```{r edit_add_code, exercise=TRUE}
3 + 4

```

Did you get 18 and 12 for your results?  If not, never fear! Press the "Start over" button to reset the code and try again.

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Arithmetic in R

In its most basic form, R can be used as a simple calculator. Consider the following arithmetic operators:

- Addition: `+`
- Subtraction: `-`
- Multiplication: `*`
- Division: `/`
- Exponentiation: `^`
- Modulo: `%%`

The last two might need some explaining:

- The `^` operator raises the number to its left to the power of the number to its right: for example `3^2` is 9.

- The modulo returns the remainder of the division of the number to the left by the number on its right, for example 5 modulo 3 or `5 %% 3` is 2.

With this knowledge, type 2 ˆ 5 to calculate 2 to the power 5. Type 28 %% 6 to calculate 28 modulo 6. Run the code.

```{r arithmetic-one, exercise=TRUE, exercise.lines = 20}
# An addition
5+5
# A subtraction
5-5
# A multiplication
3*5
# A division
(5 + 5) / 2
# Exponentiation


# Modulo



```


## Variable Assignment

A basic concept in programming is called a **variable.**

A variable allows you to store a value (e.g., 4) or an object (e.g., a function description) in R. You can then later use this variable's name to easily access the value or the object that is stored within this variable.

You can assign a value 4 to a variable `my_var` with the command. In RStudio, press `option/alt + - ` to enter the ` <- ` with appropriate spacing. Or, take the long way and type the less than symbol followed by a dash. Your choice. *Work smart, not hard.*

You can see what is stored in a variable by entering the variable name on a line by itself.

```{r var_assignment_1, echo=TRUE, exercise=FALSE, exercise.eval=TRUE}
my_var <- 4

my_var
```


#### Instructions

Complete the code in the chunk such that it assigns the value 42 to the variable `x`, and then view the contents of `x`. Notice that when you ask R to print `x`, the value 42 appears. At least it will if you did this correctly!


```{r assign_42, exercise=TRUE, exercise.lines=6, exercise.cap="Meaning of Life"}
# Assign the value 42 to x

# Print out the value of the variable x



```


Suppose you have a fruit basket with five apples. As a data analyst in training, you want to store the number of apples in a variable with the name `my_apples`.

#### Instructions

- Type the following code in the code chunk: `my_apples <- 5`. This will assign the value 5 to `my_apples`.

- Type `my_apples` below the second comment. This will print out the value of `my_apples`.

Run the code and look at the console: you see that the number 5 is printed. So R now links the variable `my_apples` to the value 5.

```{r apples1, exercise=TRUE, exercise.lines=6}
# Assign the value 5 to the variable my_apples


# Print out the value of the variable my_apples


#
```

Every tasty fruit basket needs oranges, so you decide to add six oranges. As a data analyst, your reflex is to immediately create the variable `my_oranges` and assign the value 6 to it. Next, you want to calculate how many pieces of fruit you have in total. Since you have given meaningful names to these values, you can now code this in a clear way:

```{r eval=FALSE}
my_apples + my_oranges
```


#### Instructions

- Assign to `my_oranges` the value 6, below the code for `my_apples`.

- Add the variables `my_apples` and `my_oranges` and have R print the result.

- Assign the result of adding `my_apples` and `my_oranges` to a new variable `my_fruit`.

```{r, apples_and_oranges1, exercise=TRUE, exercise.lines=15, exercise.eval=TRUE}
# Assign a value to the variables my_apples and my_oranges
my_apples <- 5


# Add these two variables together


# Create the variable my_fruit


#
```

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

